### 2020-04-23 system-model.tex
:pencil: Fix channel model

	\begin{subsection}{Composite Channel Model}
		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I' \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R \in \mathbb{C}^{K \times NL}$ respectively. At subband $n$, the frequency response of direct and reflective links write as $\boldsymbol{h}_{D,n}=[h_{D,1,n},\dots,h_{D,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{H}_{R,n}=[\boldsymbol{h}_{R,1,n}^T,\dots,\boldsymbol{h}_{R,K,n}^T]^T \in \mathbb{C}^{K \times L}$ with $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{R,k,n,L}] \in \mathbb{C}^{1 \times L}$. Similarly, the $n$-th incident channel is given by $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^T \in \mathbb{C}^{L \times 1}$. To decouple the impact of IRS operation on the incident link, we construct a block-diagonal matrix $\boldsymbol{H}_I \triangleq \mathrm{diag}\left\{\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}\right\} \in \mathbb{C}^{NL \times N}$. Element $l$ of the IRS receives a superposed waveform through the multipath channel, then redistributes it by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$. Each passive reflector absorbs a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching. On top of this, the IRS matrix per subband is constructed by collecting the reflection coefficients onto its diagonal entries as $\boldsymbol{\Theta}_0 = \mathrm{diag}\left\{\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}\right\} \in \mathbb{C}^{L \times L}$. Finally, the IRS matrix is formed by $\boldsymbol{\Theta} = \mathrm{diag}\{\underbrace{\boldsymbol{\Theta}_0,\dots,\boldsymbol{\Theta}_0}_{N\text{ times}}\} \in \mathbb{C}^{NL \times NL}$. The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, the IRS reflection matrix, and the IRS-user channel. Both direct and IRS-aided link contributes to the composite channel $\boldsymbol{H} \in \mathbb{C}^{K \times N}$ as
		\begin{equation}\label{eq:H}
			\boldsymbol{H} = \boldsymbol{H}_D+\boldsymbol{H}_R\boldsymbol{\Theta}\boldsymbol{H}_I
		\end{equation}
		whose $(k,n)$-th entry
		\begin{equation}\label{eq:h_{k,n}}
			h_{k,n}=h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
		\end{equation}
		represents the overall channel gain of user $k$ at subband $n$. On top of this, the $n$-th subchannel for all users $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ can be expressed as
		% We further define $\boldsymbol{h}_{k,n}=[\underbrace{h_{k,n},\dots,h_{k,n}}_{N\text{ times}}]^T \in \mathbb{C}^{K \times 1}$.s
		\begin{equation}\label{eq:h_n}
			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{H}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
		\end{equation}
	\end{subsection}

@@

	\begin{subsection}{Single-User Optimization}
		In this section, we first characterize the rate-energy region in the single-user setup. Define $h_n={A_n}{e^{j{\bar{\psi}_n}}}$, $w_{I,n}=s_{I,n}e^{j{\phi}_n}$, $w_{P,n}=s_{P,n}e^{j{\phi}_n}$
		, $\boldsymbol{v}=[e^{j{\theta_1}},\dots,e^{j{\theta_L}}]^H \in \mathbb{C}^{L \times 1}$, and $\boldsymbol{\Phi}_n=\mathrm{diag}\left\{\boldsymbol{h}_{R,n}\right\}\boldsymbol{h}_{I,n} \in \mathbb{C}^{L \times 1}$. On top of this, the composite channel \ref{eq:h_{k,n}} can be expressed as $h_n=h_{D,n}+\boldsymbol{v}^H{\boldsymbol{\Phi}_n}$. The WSR-E region can be obtained through a rate maximization problem subject to transmit power and output DC current constraints
		\begin{maxi}
			% {\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta}_0,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert^2}{\sigma_n^2}\right)}}{\label{op:1}}{}
			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{v}^H{\boldsymbol{\Phi}_n})w_{I,n}\rvert^2}{\sigma_n^2}\right)}}{\label{op:1}}{}
			\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
			\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho)\ge{\bar{z}}}
			\addConstraint{\lvert{v_l}\rvert=1,\quad l=1,\dots,L}
			% \addConstraint{0\le{\theta_l}\le{2{\pi}},\quad l=1,\dots,L}
		\end{maxi}
		\ref{op:1} is intricate due to the non-convex objective function, unit-modulus constraints, and coupled variables. To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that updates the phase shifts at the IRS and the information weight at the transmitter iteratively until convergence.

		The phase optimization problem is formed as follows. For a fixed information weight $\boldsymbol{w}_I$ and power-splitting ratio $\rho$, problem \ref{op:1} reduces to
		\begin{maxi}
			{\boldsymbol{v}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\lvert(h_{D,n}+\boldsymbol{v}^H{\boldsymbol{\Phi}_n})\rvert^2}{\sigma_n^2}\right)}}{\label{op:temp}}{}
			% \addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho)\ge{\bar{z}}}
			\addConstraint{\lvert{v_l}\rvert=1,\quad l=1,\dots,L}
		\end{maxi}
		Note that $\lvert(h_{D,n}+\boldsymbol{v}^H{\boldsymbol{\Phi}_n})\rvert^2=\lvert{h}_{D,n}\rvert^2+h_{D,n}\boldsymbol{\Phi}_n^H\boldsymbol{v}+\boldsymbol{v}^H\boldsymbol{\Phi}_n{h_{D,n}^*}+\boldsymbol{v}^H\boldsymbol{\Phi}\boldsymbol{\Phi}^H\boldsymbol{v}$. Introduce an auxiliary variable $t$ with unit modulus and rewrite \ref{op:temp} as
		\begin{maxi}
			{\bar{\boldsymbol{v}}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2(\lvert{h_{D,n}}\rvert^2+\bar{\boldsymbol{v}}^H\boldsymbol{R}\bar{\boldsymbol{v}})}{\sigma_n^2}\right)}}{\label{op:temp1}}{}
			\addConstraint{\lvert{\bar{v}_l}\rvert=1,\quad l=1,\dots,L+1}
		\end{maxi}
		where
		\begin{equation}
			\boldsymbol{R}=
			\begin{bmatrix}
				\boldsymbol{\Phi}_n\boldsymbol{\Phi}_n^H & \boldsymbol{\Phi}_n{h}_{D,n}^* \\
				h_{D,n}\boldsymbol{\Phi}_n               & 0
			\end{bmatrix},
			\quad \bar{\boldsymbol{v}}=
			\begin{bmatrix}
				\boldsymbol{v} \\
				t
			\end{bmatrix}
		\end{equation}
		However, problem \ref{op:temp1} is still non-convex. We further define a positive semidefinite matrix $\boldsymbol{V}=\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H$ with $\mathrm{rank}(\boldsymbol{V})=1$ such that $\bar{\boldsymbol{v}}\boldsymbol{R}\bar{\boldsymbol{v}}=\mathrm{Tr}(\boldsymbol{R}\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H)=\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})$.
		A semidefinite programming (SDP) problem is then formulated by applying SDR to drop the rank-one constraint as
		\begin{maxi}
			{\boldsymbol{V}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2(\lvert{h_{D,n}}\rvert^2+\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V}))}{\sigma_n^2}\right)}}{\label{op:temp3}}{}
			\addConstraint{\boldsymbol{V}_{l,l}=1,l=1,\dots,L+1}
			\addConstraint{\boldsymbol{V}\succeq{0}}
		\end{maxi}
		which can be solved by softwares as CVX \cite{Grant2013}.
		% It leads to a local optimum and is sensitive to the initialization of $\Theta_0$, $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$.
		% Moreover, a feasible phase design strategy that maximizes the effective composite channel is used for phase shift initialization.
		% Although the problem is non-convex, the target function can be reformulated using the triangle inequality
		% \begin{equation}
		% 	\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}w_{I,n}}\rvert
		% \end{equation}
		% where the equality holds if and only if the direct and IRS-aided links align with each other. In such case, we have $A_n=A_{D,n}+\boldsymbol{A}_{R,n}\boldsymbol{A}_{I,n}$ and and $\bar{\psi}_n=\angle{h_{D,n}}=\angle{\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}}$. Therefore, the optimal phase shift at the $l$-th reflect element is obtained in closed form
		% \begin{equation}
		% 	\theta_l^\star=\angle{h_{D,n}}-\angle{h_{R,n,l}}-\angle{h_{I,n,l}}
		% \end{equation}
		% Besides, it can be concluded from \ref{eq:R_k} and \ref{eq:z_k_standard} that the optimal information and power phases coincide at subband $n$, being matched to composite frequency response as
		% \begin{equation}\label{eq:phi_n}
		% 	\phi_{I,n}^\star=\phi_{P,n}^\star=-\bar{\psi}_n
		% \end{equation}

>>>>

	\begin{subsection}{Composite Channel Model}
		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I' \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R^H \in \mathbb{C}^{K \times NL}$ respectively. At subband $n$, the frequency response of direct and reflective links write as $\boldsymbol{h}_{D,n}=[h_{D,1,n},\dots,h_{D,K,n}]^H \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{H}_{R,n}^H=[\boldsymbol{h}_{R,1,n},\dots,\boldsymbol{h}_{R,K,n}]^H \in \mathbb{C}^{K \times L}$ with $\boldsymbol{h}_{R,k,n}^H=[h_{R,k,n,1},\dots,h_{R,k,n,L}] \in \mathbb{C}^{1 \times L}$. Similarly, the $n$-th incident channel is given by $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^H \in \mathbb{C}^{L \times 1}$. To decouple the impact of IRS operation on the incident link, we construct a block-diagonal matrix $\boldsymbol{H}_I \triangleq \mathrm{diag}\left\{\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}\right\} \in \mathbb{C}^{NL \times N}$. Element $l$ of the IRS receives a superposed waveform through the multipath channel, then redistributes it by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$. Each passive reflector absorbs a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching. On top of this, the IRS matrix per subband is constructed by collecting the reflection coefficients onto its diagonal entries as $\boldsymbol{\Theta}_0 = \mathrm{diag}\left\{\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}\right\} \in \mathbb{C}^{L \times L}$. Finally, the IRS matrix is formed by $\boldsymbol{\Theta} = \mathrm{diag}\{\underbrace{\boldsymbol{\Theta}_0,\dots,\boldsymbol{\Theta}_0}_{N\text{ times}}\} \in \mathbb{C}^{NL \times NL}$. The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, the IRS reflection matrix, and the IRS-user channel. Both direct and IRS-aided link contributes to the composite channel $\boldsymbol{H} \in \mathbb{C}^{K \times N}$ as
		\begin{equation}\label{eq:H}
			\boldsymbol{H} = \boldsymbol{H}_D+\boldsymbol{H}_R^H\boldsymbol{\Theta}\boldsymbol{H}_I
		\end{equation}
		whose $(k,n)$-th entry
		\begin{equation}\label{eq:h_{k,n}}
			h_{k,n}=h_{D,k,n}+\boldsymbol{h}_{R,k,n}^H\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
		\end{equation}
		represents the overall channel gain of user $k$ at subband $n$. On top of this, the $n$-th subchannel for all users $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ can be expressed as
		% We further define $\boldsymbol{h}_{k,n}=[\underbrace{h_{k,n},\dots,h_{k,n}}_{N\text{ times}}]^T \in \mathbb{C}^{K \times 1}$.s
		\begin{equation}\label{eq:h_n}
			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{H}_{R,n}^H\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
		\end{equation}
		Define $\boldsymbol{v}=[e^{j{\theta_1}},\dots,e^{j{\theta_L}}]^H \in \mathbb{C}^{L \times 1}$ and $\boldsymbol{\Phi}_n^H=\boldsymbol{H}_{R,n}^H\mathrm{diag}\left\{\boldsymbol{h}_{I,n}\right\} \in \mathbb{C}^{K \times L}$. Therefore, \ref{eq:h_n} rewrites as
		\begin{equation}
			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}
		\end{equation}
	\end{subsection}

@@

	\begin{subsection}{Single-User Optimization}
		In this section, we first characterize the rate-energy region in the single-user setup. Let $h_n={A_n}{e^{j{\bar{\psi}_n}}}$, $w_{I,n}=s_{I,n}e^{j{\phi}_n}$, $w_{P,n}=s_{P,n}e^{j{\phi}_n}$. The WSR-E region can be obtained through a rate maximization problem subject to transmit power and output DC current constraints
		\begin{maxi}
			% {\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta}_0,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert^2}{\sigma_n^2}\right)}}{\label{op:1}}{}
			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert(h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v})w_{I,n}\rvert^2}{\sigma_n^2}\right)}}{\label{op:1}}{}
			\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
			\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho)\ge{\bar{z}}}
			\addConstraint{\lvert{v_l}\rvert=1,\quad l=1,\dots,L}
			% \addConstraint{0\le{\theta_l}\le{2{\pi}},\quad l=1,\dots,L}
		\end{maxi}
		\ref{op:1} is intricate due to the non-convex objective function, unit-modulus constraints, and coupled variables. To reduce the design complexity, we propose an suboptimal alternating optimization algorithm that updates the phase shifts at the IRS and the information weight at the transmitter iteratively until convergence.

		The phase optimization problem is formed as follows. For a fixed information weight $\boldsymbol{w}_I$ and power-splitting ratio $\rho$, problem \ref{op:1} reduces to
		\begin{maxi}
			{\boldsymbol{v}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\lvert{h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}}\rvert^2}{\sigma_n^2}\right)}}{\label{op:temp}}{}
			% \addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{v},\rho)\ge{\bar{z}}}
			\addConstraint{\lvert{v_l}\rvert=1,\quad l=1,\dots,L}
		\end{maxi}
		Since $\lvert{h_{D,n}+\boldsymbol{\Phi}_n^H\boldsymbol{v}}\rvert^2=\lvert{h_{D,n}}\rvert^2+h_{D,n}^*\boldsymbol{\Phi}_n^H\boldsymbol{v}+\boldsymbol{v}^H\boldsymbol{\Phi}_n{h_{D,n}}+\boldsymbol{v}^H\boldsymbol{\Phi}\boldsymbol{\Phi}^H\boldsymbol{v}$, we introduce an auxiliary variable $t$ with unit modulus and transform \ref{op:temp} to
		\begin{maxi}
			{\bar{\boldsymbol{v}}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2(\bar{\boldsymbol{v}}^H\boldsymbol{R}\bar{\boldsymbol{v}})}{\sigma_n^2}\right)}}{\label{op:temp1}}{}
			\addConstraint{\lvert{\bar{v}_l}\rvert=1,\quad l=1,\dots,L+1}
		\end{maxi}
		where
		\begin{equation}
			\boldsymbol{R}=
			\begin{bmatrix}
				\boldsymbol{\Phi}_n\boldsymbol{\Phi}_n^H & h_{D,n}^*{\boldsymbol{\Phi}_n^H} \\
				\boldsymbol{\Phi}_n{h_{D,n}}             & h_{D,n}^*{h_{D,n}}
			\end{bmatrix},
			\quad \bar{\boldsymbol{v}}=
			\begin{bmatrix}
				\boldsymbol{v} \\
				t
			\end{bmatrix}
		\end{equation}
		However, problem \ref{op:temp1} is still non-convex. We further define a positive semidefinite matrix $\boldsymbol{V}=\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H$ with $\mathrm{rank}(\boldsymbol{V})=1$ such that $\bar{\boldsymbol{v}}\boldsymbol{R}\bar{\boldsymbol{v}}=\mathrm{Tr}(\boldsymbol{R}\bar{\boldsymbol{v}}\bar{\boldsymbol{v}}^H)=\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})$.
		A semidefinite programming (SDP) problem is then formulated by dropping the rank-one constraint
		\begin{maxi}
			{\boldsymbol{V}}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{w}_{I,n}\rvert^2\mathrm{Tr}(\boldsymbol{R}\boldsymbol{V})}{\sigma_n^2}\right)}}{\label{op:temp3}}{}
			\addConstraint{\boldsymbol{V}_{l,l}=1,l=1,\dots,L+1}
			\addConstraint{\boldsymbol{V}\succeq{0}}
		\end{maxi}
		which can be solved by softwares as CVX \cite{Grant2013}. [Use random vector or rank reduction method to extract $\boldsymbol{v}$ from $\boldsymbol{V}$]
		% It leads to a local optimum and is sensitive to the initialization of $\Theta_0$, $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$.
		% Moreover, a feasible phase design strategy that maximizes the effective composite channel is used for phase shift initialization.
		% Although the problem is non-convex, the target function can be reformulated using the triangle inequality
		% \begin{equation}
		% 	\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}w_{I,n}}\rvert
		% \end{equation}
		% where the equality holds if and only if the direct and IRS-aided links align with each other. In such case, we have $A_n=A_{D,n}+\boldsymbol{A}_{R,n}\boldsymbol{A}_{I,n}$ and and $\bar{\psi}_n=\angle{h_{D,n}}=\angle{\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}}$. Therefore, the optimal phase shift at the $l$-th reflect element is obtained in closed form
		% \begin{equation}
		% 	\theta_l^\star=\angle{h_{D,n}}-\angle{h_{R,n,l}}-\angle{h_{I,n,l}}
		% \end{equation}
		% Besides, it can be concluded from \ref{eq:R_k} and \ref{eq:z_k_standard} that the optimal information and power phases coincide at subband $n$, being matched to composite frequency response as
		% \begin{equation}\label{eq:phi_n}
		% 	\phi_{I,n}^\star=\phi_{P,n}^\star=-\bar{\psi}_n
		% \end{equation}

		Once a feasible phase shift set is obtained, the original problem \ref{op:1} is reduced to
		\begin{maxi}
			% {\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)(A_{D,n}+\boldsymbol{A}_{R,n}\boldsymbol{A}_{I,n})^2{s_{I,n}^2}}{\sigma_n^2}\right)}}{\label{op:2}}{}
			{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)A_n^2{s_{I,n}^2}}{\sigma_n^2}\right)}}{\label{op:2}}{}
			\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
			\addConstraint{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)\ge{\bar{z}}}
		\end{maxi}
		\begin{figure*}[b]
			\hrule
			\begin{equation}\label{eq:z_gp}
				\begin{split}
					z
					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{A_n^2(s_{I,n}^2+s_{P,n}^2)}+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{A_{n_1}A_{n_2}A_{n_3}A_{n_4}(2s_{I,n_1}s_{I,n_2}s_{I,n_3}s_{I,n_4}+s_{P,n_1}s_{P,n_2}s_{P,n_3}s_{P,n_4})}\\
					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{{A_n^4}{s_{I,n}^2}{s_{P,n}^2}}
				\end{split}
			\end{equation}
		\end{figure*}
		with $z$ given by \ref{eq:z_gp}. It can be transformed to an equivalent problem by introducing an auxiliary variable $t_0$
		\begin{mini}
			{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\frac{1}{t_0}}{\label{op:3}}{}
			\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
			\addConstraint{\frac{t_0}{\prod_{n}{\left(1+\frac{(1-\rho){A_n^2}{s_{I,n}^2}}{\sigma_n^2}\right)}}\le{1}}
			\addConstraint{\frac{\bar{z}}{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}\le{1}}
		\end{mini}
		\ref{op:3} is a Reversed Geometric Program which can be transformed to standard Geometric Program (GP). The basic idea is to decompose the information and power posynomials as sum of monomials, then derive their upper bounds using Arithmetic Mean-Geometric Mean (AM-GM) inequality \cite{Clerckx2018b,Chiang2005}. Let $z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)=\sum_{{m_P}=1}^{M_P}{g_{P,m_P}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}$, problem \ref{op:3} is equivalent to
		% $1+\bar{\rho}{A_n^2}{s_{I,n}^2}/\sigma_n^2=\sum_{{m_{I,n}}=1}^{M_{I,n}}{g_{I,m_{I,n}}(\boldsymbol{s}_I,\bar{\rho})}$
		\begin{mini}
			{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\frac{1}{t_0}}{\label{op:4}}{}
			\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
			\addConstraint{{t_0}\prod_{n}{\left(\frac{1}{\gamma_{I,n,1}}\right)^{-\gamma_{I,n,1}} \left(\frac{\bar{\rho}{A_n^2}{s_{I,n}^2}}{{\sigma_n^2}{\gamma_{I,n,2}}}\right)^{-\gamma_{I,n,2}}}\le{1}}
			\addConstraint{\bar{z}\prod_{m_P}{\left(\frac{g_{P,m_P}(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)}{\gamma_{P,m_P}}\right)^{-\gamma_{P,m_P}}}\le{1}}
			\addConstraint{\rho+\bar{\rho}\le{1}}
		\end{mini}
		where $\gamma_{I,n,1},\gamma_{I,n,2} \ge 0$, $\gamma_{I,n,1}+\gamma_{I,n,2}=1$, $\gamma_{P,m_P} \ge 0,\forall m_P=1,\dots,M_P$ and $\sum_{{m_P}=1}^{M_P}{\gamma_{m_P}}=1$. As suggested in \cite{Clerckx2018b}, the tightness of the AM-GM inequality depends on $\{\gamma_{I,n},\gamma_P\}$ that require iterative update. At iteration $i$, we choose
		\begin{align}
			\gamma_{I,n,1}^{(i)} & =\frac{1}{1+\frac{\bar{\rho}^{(i-1)}{A_n^2}{s_{I,n}^{(i-1)}}^2}{\sigma_n^2}},                                                                         &  & n=1,\dots,N,    \\
			\gamma_{I,n,2}^{(i)} & =\frac{\frac{\bar{\rho}^{(i-1)}{A_n^2}{s_{I,n}^{(i-1)}}^2}{\sigma_n^2}}{1+\frac{\bar{\rho}^{(i-1)}{A_n^2}{s_{I,n}^{(i-1)}}^2}{\sigma_n^2}},           &  & n=1,\dots,N,    \\
			\gamma_{P,m_P}^{(i)} & =\frac{g_{P,m_P}(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}{z(\boldsymbol{s}_I^{(i-1)},\boldsymbol{s}_P^{(i-1)},\rho^{(i-1)})}, &  & m_P=1,\dots,M_P
		\end{align}
		and then solve problem \ref{op:4}.
	\end{subsection}
\end{section}
